---
title: "HW1"
author: "Yuelin Long"
date: "February 17, 2019"
output: html_document
---

## Problem 1
```{r}
library(tidyverse)
#Data import
x = rep(0:4)
y = c(2,8,15,23,27)
m = rep(30,5)
resp = cbind(y,m-y)
```
###Question 1
```{r}
# Modeling
## fit logistic model
glm_logit=glm(resp~x, family=binomial(link='logit'))

sol_11 = function(model, ref){
b1 = model %>% 
  broom::tidy() %>% 
  filter(term == 'x') %>% 
  select(estimate) %>% 
  as.numeric()

b0 = model %>% 
  broom::tidy() %>% 
  filter(term == '(Intercept)') %>% 
  select(estimate) %>% 
  as.numeric()

b_se = model %>% 
  broom::tidy() %>% 
  filter(term == 'x') %>% 
  select(std.error) %>% 
  as.numeric()

b_lower_ci = b1 + b_se * qnorm(0.025)
b_upper_ci = b1 - b_se * qnorm(0.025)

dev = model %>% 
  broom::glance() %>% 
  select(deviance) %>% 
  as.numeric()

if (ref == 1){
  p = exp(b0 + b1*0.01) / (1+exp(b0 + b1*0.01))
} else if (ref == 2){
  p = pnorm((b0 + b1*0.01))
} else {
  p = 1- exp(-exp(b0 + b1*0.01))
}

print(c(b1, b_lower_ci, b_upper_ci, dev, p))
}

## fit a probit model
glm_probit=glm(resp~x, family=binomial(link='probit')) 
## fit a complementary log log model
glm_clog=glm(resp~x, family=binomial(link='cloglog'))
```

The result for question 1 is as follows (order by stimateof β, CI for β: lower to upper, Deviance, p(dying|x= 0.01)):
```{r}
#Print problem 1 question 1
print("logit")
sol_11(glm_logit,1)


print("probit")
sol_11(glm_probit,2)

print("clog")
sol_11(glm_clog,3)

```

###Question 2
```{r}
sol_12 = function(model,ref){
b1 = model %>% 
  broom::tidy() %>% 
  filter(term == 'x') %>% 
  select(estimate) %>% 
  as.numeric()

b0 = model %>% 
  broom::tidy() %>% 
  filter(term == '(Intercept)') %>% 
  select(estimate) %>% 
  as.numeric()

betacov=vcov(model) # inverse fisher information

if (ref == 1){
  g_50 = log(0.5/(1-0.5))
} else if (ref == 2){
  g_50 = qnorm(0.5)
} else {
  g_50 = log(-log(1-0.5))
}

x0fit = (g_50 - b0)/b1
point_est = exp(x0fit) # point estimate of LD50
varx0=betacov[1,1]/(b1^2)+betacov[2,2]*((b0-g_50)^2)/(b1^4)-2*betacov[1,2]*(b0-g_50)/(b1^3)
#90% CI
x0_upper = exp((x0fit-qnorm(0.05)*sqrt(varx0)))
x0_lower = exp((x0fit+qnorm(0.05)*sqrt(varx0)))
print(c(point_est, x0_lower, x0_upper))
}

#Print problem 1 question 2: LD50 95% Confidence Interval
print("logit")
sol_12(glm_logit,1)

print("probit")
sol_12(glm_probit,2)

print("clog")
sol_12(glm_clog,3)
```


## Problem 2
```{r}
#Data import
x = seq(10000,90000,5000)
y = c(0,2,4,2,12,14,10,7,5,5,3,5,2,0,4,2,1)
m = c(4,6,10,12,39,36,22,14,10,12,8,9,3,1,5,2,1)
resp = cbind(y,m-y)
n = 10
p = 2

#Modeling
glm_logit=glm(resp~x, family=binomial(link='logit'))
summary(glm_logit)

#Coefficient
b1 = glm_logit %>% 
  broom::tidy() %>% 
  filter(term == 'x') %>% 
  select(estimate) %>% 
  as.numeric()
b0 = glm_logit %>% 
  broom::tidy() %>% 
  filter(term == '(Intercept)') %>% 
  select(estimate) %>% 
  as.numeric()
b_se = glm_logit %>% 
  broom::tidy() %>% 
  filter(term == 'x') %>% 
  select(std.error) %>% 
  as.numeric()

#Goodness of fit: due to the number in different groups is small (mostly smaller than 10), use Hosmer and Lemeshow goodness of fit (GOF) test

library(ResourceSelection)
hoslem.test(glm_logit$y, fitted(glm_logit), g=10) 

test_stat = hoslem.test(glm_logit$y, fitted(glm_logit), g=10) %>% 
  broom::glance() %>% 
  select(statistic) %>% 
  as.numeric()
test_stat

critical_value = qchisq(0.95,n-p)
critical_value
```

### Question 1
As we can see, the test statistics is `r test_stat`, while the critical value is `r critical_value`. Since the test statistics is smaller than critical value, we fail to reject null, and believe that the model is a good fit.

It is also proved by the large p value.

### Question 2
For 1 dollar change of the scholarship amount, the log odds of enrollment would increase by `r b1`. The confidence interval is (`r b1 + b_se * qnorm(0.025)`, `r b1 - b_se * qnorm(0.025)`)

### Question 3
```{r}
#Enrollment rate is 40%, meaning log(0.4/1-0.4) = b0 + b1*x. Solve for x
g_40 = log(0.4/(1-0.4)) 
x0fit = (g_40 - b0)/b1
#Confidence interval
betacov=vcov(glm_logit) # inverse fisher information
varx0=betacov[1,1]/(b1^2)+betacov[2,2]*((b0-g_40)^2)/(b1^4)-2*betacov[1,2]*(b0-g_40)/(b1^3)
#95% CI
x0_upper = x0fit-qnorm(0.025)*sqrt(varx0)
x0_lower = x0fit+qnorm(0.025)*sqrt(varx0)
print(c(x0fit, x0_lower, x0_upper))

```

To get 40% yield rate, we should provide $`r x0fit` scholarship, with a confidence interval to be (`r x0_lower`, `r x0_upper`)
